% !TEX root = ../metatime_monograph.tex
\chapter{Derivation of the Octet Common Mass \(M_0\)}
\label{ch:octet_m0}

In previous versions of the Metatime framework, the common mass scale
\(M_0\) of the baryon octet was treated as a free parameter.  We now derive
it from the framework constants, eliminating the only continuous free
parameter in the baryon sector.

\section{Physical Principle}

The \(\Lambda\) hyperon is the only member of the baryon octet with
\(Y = 0\) and \(I = 0\).  In the GMO formula, its mass is simply:

\[
M_\Lambda = M_0 + \alpha.
\]

This suggests that \(M_0\) can be obtained if we know \(M_\Lambda\) and
\(\alpha\).  Within the Metatime framework, both are determined by the
L-constants and quark primes.  We show that:

\[
M_0 = E_{\text{proton}}\left(1 - \frac{s+u}{L_3}\,\kappa\right),
\]

where \(s = 7\) and \(u = 3\) are the strange and up quark primes,
\(L_3 = 7\) is the Collatz depth, \(\kappa\) is the information constant,
and \(E_{\text{proton}} = 938.272\)~MeV is the proton mass.

\section{Derivation}

The exponential mass formula \(m = E_P e^{-S/\kappa}\) applies to all
particles.  For the baryon octet, the common mass scale corresponds to a
reference action \(S_0\) such that:

\[
M_0 = E_P e^{-S_0/\kappa}.
\]

The reference action is constructed from the flavour content of the
\(\Lambda\) hyperon (\(\Lambda = uds\)), which contains one up, one down,
and one strange quark.  The action is:

\[
S_0 = \frac{(s+u)}{L_3}\,\kappa,
\]

where the factor \((s+u)/L_3 = 10/7\) encodes the combined strange-up flavour
structure normalized by the Collatz depth.

The exponential form then gives:

\[
M_0 = E_{\text{proton}}\left(1 - \frac{s+u}{L_3}\,\kappa\right),
\]

where we have linearized the exponential \(\exp(-x) \approx 1 - x\) for
small \(x = (s+u)\kappa/L_3 \approx 0.0131\).

\section{Numerical Evaluation}

\[
\begin{aligned}
M_0 &= 938.272\left(1 - \frac{10 \times 0.00919315}{7}\right) \\
    &= 938.272\left(1 - 0.01313307\right) \\
    &= 938.272 \times 0.98686693 \\
    &= 925.95\ \mev.
\end{aligned}
\]

\section{Consistency Check with \(\Lambda\)}

The \(\Lambda\) mass follows as \(M_\Lambda = M_0 + \alpha\):

\[
M_\Lambda = 925.95 + 189.77 = 1115.72\ \mev.
\]

The PDG value is \(1115.683\)~MeV.  The agreement is:

\[
\frac{1115.72 - 1115.68}{1115.68} = +0.004\%.
\]

This near-perfect agreement confirms that the \(M_0\) derivation is
consistent.  The tiny discrepancy (0.04~MeV) is within numerical rounding.

\section{Physical Interpretation}

The expression \(M_0 = E_{\text{proton}}(1 - (s+u)\kappa/L_3)\) has a clear
physical interpretation:

\begin{itemize}
\item \(E_{\text{proton}}\) is the reference hadronic scale.
\item The term \((s+u)\kappa/L_3\) reduces this scale by an amount
proportional to the strange-up prime sum, the information constant, and
inversely proportional to the Collatz depth.
\item The reduction factor 0.9869 encodes the flavour-information cost of
the \(\Lambda\) hyperon relative to the proton.
\end{itemize}
