% !TEX root = ../metatime_monograph.tex
\chapter{Derivation of the Decuplet Common Mass \(M_0'\)}
\label{ch:decuplet_m0prime}

The baryon decuplet (spin-3/2) is heavier than the octet (spin-1/2) by a
flavour-related offset.  We derive the decuplet common mass scale \(M_0'\)
from the same framework constants as the octet scale.

\section{Physical Principle}

The decuplet consists of spin-3/2 baryons: the \(\Delta\) (isospin 3/2),
the \(\Sigma^*\) (isospin 1), the \(\Xi^*\) (isospin 1/2), and the
\(\Omega^-\) (isospin 0).  Unlike the octet, the decuplet satisfies an
equal-spacing rule in hypercharge \(Y\).

The \(\Omega^-\) baryon (\(sss\), \(Y=-2\)) is the heaviest and most
symmetric member of the decuplet.  Its mass provides the anchor for the
decuplet scale.

\section{Derivation}

The decuplet common mass is:

\begin{equation}
M_0' \equiv E_{\text{proton}}\bigl(1 + (s-u)\,\kappa\bigr).
\label{eq:M0prime}
\end{equation}

The positive sign reflects the greater mass of the spin-3/2 multiplet
relative to the spin-1/2 octet.  The difference \((s-u) = 7-3 = 4\) is
the strange-up prime difference, which sets the flavour-induced mass
offset.

\section{Numerical Evaluation}

\[
\begin{aligned}
M_0' &= 938.272\,(1 + 4 \times 0.00919315) \\
     &= 938.272 \times 1.0367726 \\
     &= 972.72\ \mev.
\end{aligned}
\]

\section{Comparison with the Octet Scale}

\[
\begin{aligned}
M_0\ (\text{octet}) &= 925.95\ \mev, \\
M_0'\ (\text{decuplet}) &= 972.72\ \mev.
\end{aligned}
\]

The decuplet scale is \(46.77\)~MeV (\(5.0\%\)) heavier than the octet
scale.  This mass gap arises from the spin-spin interaction between
quarks: spin-3/2 configurations have aligned spins, which increases the
chromomagnetic energy relative to spin-1/2 configurations.

\section{Consistency Check with \(\Omega^-\)}

The \(\Omega^-\) mass follows from the decuplet formula:

\[
M_{\Omega^-} = M_0' + \alpha_{10} + \beta_{10}(-2).
\]

With \(\alpha_{10} = 405.41\)~MeV and \(\beta_{10} = -150.95\)~MeV
(Chapter~\ref{ch:decuplet_predictions}):

\[
M_{\Omega^-} = 972.72 + 405.41 + 301.90 = 1680.03\ \mev.
\]

The PDG value is \(1672.45\)~MeV.  The agreement is:

\[
\frac{1680.03 - 1672.45}{1672.45} = +0.45\%.
\]

This confirms that the \(M_0'\) derivation captures the decuplet mass scale
correctly, though with a small systematic offset that propagates through
the equal-spacing rule.
