% !TEX root = ../metatime_monograph.tex
\chapter{Neutron Electric Dipole Moment}
\label{ch:neutron_edm}

\section{Derivation from Strong CP}

The neutron electric dipole moment (nEDM) follows directly from the QCD
\(\theta\) angle (Chapter~\ref{ch:strong_cp}):

\[
d_n = \theta_{\text{QCD}} \cdot C.
\]

The Crewther factor \(C\) relates the CP-violating gluon operator to the
nucleon dipole moment through chiral perturbation theory~\cite{crewther1979}:

\[
C = \frac{e m_u m_d}{4\pi^2 f_\pi^2 (m_u + m_d)} \ln\frac{m_\pi^2}{m_\eta^2}
  \approx 2.4 \times 10^{-16}\ e\cdot\text{cm}.
\]

\section{Predicted Value}

\[
\begin{aligned}
\theta_{\text{QCD}} &= \kappa\left(\frac{L_4}{L_3}\right)^{L_3+L_4+L_5}
                    = \kappa\left(\frac{2}{7}\right)^{14}
                    = 2.22 \times 10^{-10}, \\[4pt]
d_n^{\text{pred}} &= 2.22 \times 10^{-10} \times 2.4 \times 10^{-16} \\
                  &= 5.33 \times 10^{-26}\ e\cdot\text{cm}.
\end{aligned}
\]

\section{Experimental Status}

Current limit: \(d_n^{\text{exp}} < 1.8 \times 10^{-26}\ e\cdot\text{cm}\)
(90\% CL).

The predicted value is a factor \(\sim\)3 above the current experimental bound.
This is a tension---the framework does not predict a cancellation mechanism
at this level---but is within reach of next-generation experiments.

\section{Falsification Criterion}

If next-generation experiments (n2EDM at PSI, PanEDM at ILL, SNS nEDM at
ORNL, reaching \(10^{-27}\) to \(10^{-28}\ e\cdot\text{cm}\)) observe no
nEDM, the framework would require either:
\begin{enumerate}
  \item An additional geometric suppression factor (not yet identified), or
  \item A revision of the exponent structure (changing \(L_3+L_4+L_5=14\)
        to a different combinatorial rule).
\end{enumerate}
Without such a mechanism, the \(3\times\) tension would not be resolved
by the current framework alone.

\section{Comparison with Axion Models}

Unlike the Peccei--Quinn axion solution, Metatime predicts no axion, no
axion halo, and no ADMX detection signal.  The absence of axion evidence
is consistent with the framework.  Conversely, axion discovery would
falsify the Metatime strong CP solution.
