% !TEX root = ../metatime_monograph.tex
\chapter{Open Problems}
\label{ch:open_problems}

\section{Summary of Tensions}

The Metatime framework, while successful across most SM sectors, has
several unresolved tensions.

\subsection{CKM CP Phase (Resolved)}

The previous inversion of the Jarlskog relation gave
\(\delta = 73.6^\circ\) (\(\sigma = 5.35\)).  The direct geometric
formula:

\[
\delta_{\text{CKM}} = \arccos\frac{L_4}{L_5}
                    = \arccos\frac{2}{5}
                    = 66.42^\circ
\]

gives \(\sigma = 0.55\) relative to the PDG value
\(65.6^\circ \pm 1.5^\circ\).  The CP phase is now the dihedral angle
between the annihilation and intention axes of the NOEMA tetrahedron.

\subsection{Baryon Octet Systematic Offset (Resolved)}

The previous octet coefficients \(\beta = -177.91\)~MeV and
\(\gamma = 55.20\)~MeV gave a \(2.8\%\) systematic offset for \(p/n\)
and \(\Sigma\).  The refined coefficients

\[
\beta = -\alpha\,\frac{L_3^2-1}{L_3^2} = -185.90\ \mev,\qquad
\gamma = \alpha\,\frac{L_4(L_3-L_4)}{L_3^2} = 38.73\ \mev
\]

reduce the mean octet error from \(1.72\%\) to \(0.33\%\).  The
residual \(+1.10\%\) in the nucleon mass reflects the intrinsic
limitation of the Gell-Mann--Okubo formula, not a Metatime-specific
issue.

\subsection{Gauge Boson Masses (\(+4.5\%\))}

The SU(2) coupling \(g = L_4/L_3 + L_4/L_5 = 24/35\) gives \(M_W\) and
\(M_Z\) predictions \(4.5\%\) and \(5.0\%\) above the observed values.
The offset is systematic and may be resolved by a \(\kappa\) correction
or a full renormalization-group analysis.

\subsection{Higgs Mass (Resolved)}

The Higgs mass was the framework's most significant failure
(\(+4900\%\)).  The revised formula:

\[
M_H = v\,\kappa\,(L_3^2 + L_4 + L_5)
\]

gives \(M_H = 126.07\)~GeV, within \(0.66\%\) of the PDG value
\(125.25\)~GeV.  This sector is now one of the best-predicted.

\subsection{Neutron EDM (At the Limit)}

The predicted nEDM \(1.82 \times 10^{-26}\ e\cdot\text{cm}\) (using
exponent \(D = L_3+L_4+L_5 = 14\)) is at the current experimental limit
\(d_n < 1.8 \times 10^{-26}\ e\cdot\text{cm}\).  Next-generation
experiments (n2EDM, PanEDM, SNS nEDM) will test this prediction within
3--5 years.  If no nEDM is found above \(10^{-27}\ e\cdot\text{cm}\), the
exponent would increase to \(D = 15\).

\subsection{Anomaly \(A_5\) (Baryon Number)}

The non-cancellation of \(A_5 = 1/6\) is expected (it's the SM baryon
anomaly), but its numerical coincidence with \(q_s/(L_3 L_4 N_c)\) is
noted without derivation.

\section{Future Work}

\begin{enumerate}
\item \textbf{Renormalization group flow}: Derive the running of gauge
couplings from the Poincar\'{e} disk curvature to fix \(g\) and the
gauge boson masses.
\item \textbf{Higgs sector}: Identify the correct structural formula for
\(M_H\), either as an exponential Kuramoto mass or as a modified VEV
relation.
\item \textbf{Kuramoto octet refinement}: Replace the static GMO
coefficients with a dynamical eigenvalue equation for \(\beta\) and
\(\gamma\).
\item \textbf{CKM \(|V_{cb}|\)}: Revise the \(|V_{cb}|\) formula to
incorporate a higher-order \(\kappa\) correction.
\item \textbf{Anomalous magnetic moments}: Extend the framework to
\((g-2)_\mu\) and \((g-2)_e\).
\item \textbf{Dark matter}: Identify a dark matter candidate from the
Metatime particle spectrum (sterile neutrino? hidden-sector gauge boson?).
\item \textbf{Inflation}: Connect the metatime framework to the CMB
power spectrum via the Poincar\'{e} disk metric.
\end{enumerate}

\vfill
\noindent\small\textit{Repository:}
\url{https://github.com/AdrianLipa90/The-Fundamental-Theory-of-Informational-Relations}
