% !TEX root = ../metatime_monograph.tex
\chapter{Derivation of $\kappa = \ln 2 / (24\pi)$}
\label{app:kappa}

\section{Shannon Information}

The fundamental unit of information is the binary choice: the answer to a
yes/no question, encoded as a single bit.  Claude Shannon proved in 1948
that the entropy of a discrete random variable $X$ with $n$ equally
likely outcomes is~\cite{shannon1948}:

\[
H(X) = \log_2 n \quad (\text{bits}).
\]

For $n=2$ (a single binary decision), $H = \log_2 2 = 1$ bit.  In natural
units (nats), this is $H = \ln 2$ nats.  This is the irreducible
information cost of distinguishing two quantum states.

\section{Phase-Space Volume of $\mathbb{C}P^3$}

The projective Hilbert space of three-flavour SU(3) colour is
$\mathbb{C}P^{3}$, a K\"{a}hler manifold of real dimension 6.  Its
symplectic volume (the integral of the K\"{a}hler form $\omega$ over the
manifold) is:

\[
\text{Vol}(\mathbb{C}P^{3}) = \frac{\pi^3}{3!} = \frac{\pi^3}{6}.
\]

However, the relevant phase space for the Berry phase is the space of
pure colour states modulo the $S(U(1) \times U(2))$ little group, which
yields the quotient $\mathbb{C}P^{2}$ for a single colour direction.

The tetrahedral discrete holonomy $A_4$ (the symmetry of the three
lepton generations) has order 12.  When combined with the two possible
spin orientations (Berry's original spin-1/2 in a magnetic field), the
full denominator becomes:

\[
24\pi = 2 \times 12 \times \pi,
\]

where $\pi$ is the solid angle of the Bloch sphere for a spin-1/2 system
(Berry's original phase).

\section{The Ratio}

Combining the information numerator and the geometric denominator:

\[
\kappa \equiv \frac{\ln 2}{24\pi}.
\]

Numerically:

\[
\kappa = \frac{0.6931471805599453}{75.39822368615503}
       = 0.00919315000636\ldots
\]

\section{Why $24\pi$?  A Deeper View}

The denominator decomposes as:

\[
24\pi = \underbrace{8}_{\text{gluons}} \times
        \underbrace{3}_{\text{colours}} \times
        \underbrace{\pi}_{\text{Bloch half-sphere}}.
\]

Equivalently:

\[
24\pi = \underbrace{4\pi}_{\text{full Bloch sphere}} \times
        \underbrace{6}_{\text{Coxeter number of }A_4}.
\]

The tetrahedral group $A_4$ has Coxeter number $h = 6$, and the order
of the corresponding reflection group is $24 = 6 \times 4$.  This is
the same 24 that appears in the modular $j$-invariant, the Leech lattice,
and the number of generations in the fermion spectrum.

\section{No Free Parameter}

$\kappa$ is not fitted to experimental data.  It is computed directly
from two mathematical constants ($\ln 2$ and $\pi$) and two structural
choices (the Coxeter number 6 and the spin factor 2).  There is no
continuous degree of freedom.
