%% Metatime Monograph
%% Complete derivations of all Standard Model parameters from
%% the Metatime framework: κ = ln(2)/(24π), L₃=7, L₄=2, L₅=5
%%
%% Adrian Lipa, Doncaster, UK
%% Version 9.0 — Full Monograph
%%
%% Compile: pdflatex metatime_monograph.tex 
%%          && pdflatex metatime_monograph.tex
%%          && pdflatex metatime_monograph.tex

\documentclass[11pt,a4paper,twoside]{book}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm,bm,mathtools}
\usepackage{slashed}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{makeidx}
\usepackage{verbatim}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage[
  left=2.5cm, right=2.5cm, top=3cm, bottom=3cm,
  headheight=14pt
]{geometry}

\makeindex

\theoremstyle{definition}
\newtheorem{definition}{Definition}[chapter]
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}{Lemma}[chapter]

\newcommand{\OI}{\kappa}
\newcommand{\Lam}{\Lambda}
\newcommand{\mev}{\,\text{MeV}}
\newcommand{\gev}{\,\text{GeV}}
\newcommand{\eV}{\,\text{eV}}
\newcommand{\PDG}[1]{\ensuremath{#1^{\text{PDG}}}}
\newcommand{\pdgsup}{\ensuremath{^{\text{PDG}}}}
\newcommand{\Eproton}{E_{\text{proton}}}
\newcommand{\Eplanck}{E_{P}}
\newcommand{\keV}{\,\text{keV}}
\newcommand{\tev}{\,\text{TeV}}
\newcommand{\SM}{\text{SM}}

\begin{document}

\frontmatter

\title{Metatime: A Complete Derivation of the Standard Model \\
       from Geometric Phase Information Theory}
\author{Adrian Lipa}
\date{Independent Researcher, Doncaster, UK\\\today}

\maketitle

\tableofcontents

\mainmatter

%% ======================================================================
%% PART I — FOUNDATIONS
%% ======================================================================
\part{Foundations}

\include{chapters/ch01_introduction}
\include{chapters/ch02_metatime_framework}
\include{chapters/ch03_l_constants}
\include{chapters/ch04_quark_primes}

%% ======================================================================
%% PART II — CHARGED LEPTONS
%% ======================================================================
\part{Charged Leptons}

\include{chapters/ch05_electron_action}
\include{chapters/ch06_generation_release}
\include{chapters/ch07_lepton_spectrum}

%% ======================================================================
%% PART III — BARYONS
%% ======================================================================
\part{Baryons}

\include{chapters/ch08_gmo_formula}
\include{chapters/ch09_octet_m0}
\include{chapters/ch10_octet_coefficients}
\include{chapters/ch11_octet_predictions}
\include{chapters/ch12_decuplet_m0prime}
\include{chapters/ch13_decuplet_predictions}

%% ======================================================================
%% PART IV — MESONS
%% ======================================================================
\part{Mesons}

\include{chapters/ch14_pseudoscalar_mesons}
\include{chapters/ch15_heavy_mesons}

%% ======================================================================
%% PART V — NEUTRINOS
%% ======================================================================
\part{Neutrinos}

\include{chapters/ch16_pmns_mixing}
\include{chapters/ch17_neutrino_masses}

%% ======================================================================
%% PART VI — CKM QUARK MIXING
%% ======================================================================
\part{CKM Quark Mixing}

\include{chapters/ch18_ckm_matrix}
\include{chapters/ch19_ckm_cp_violation}

%% ======================================================================
%% PART VII — ELECTROWEAK SECTOR
%% ======================================================================
\part{Electroweak Sector}

\include{chapters/ch20_higgs_vev}
\include{chapters/ch21_weinberg_angle}
\include{chapters/ch22_fine_structure}
\include{chapters/ch23_gauge_bosons}
\include{chapters/ch24_higgs_mass}

%% ======================================================================
%% PART VIII — STRONG CP
%% ======================================================================
\part{Strong CP Problem}

\include{chapters/ch25_strong_cp_angle}
\include{chapters/ch26_neutron_edm}

%% ======================================================================
%% PART IX — ANOMALIES
%% ======================================================================
\part{Gauge Anomalies}

\include{chapters/ch27_hypercharge}
\include{chapters/ch28_anomaly_cancellation}

%% ======================================================================
%% PART X — COSMOLOGY
%% ======================================================================
\part{Cosmology}

\include{chapters/ch29_dark_energy}

%% ======================================================================
%% PART XI — CONCLUSIONS
%% ======================================================================
\part{Conclusions}

\include{chapters/ch30_parameter_summary}
\include{chapters/ch31_open_problems}

%% ======================================================================
%% APPENDICES
%% ======================================================================
\appendix

\include{appendices/appA_kappa_derivation}
\include{appendices/appB_collatz_tables}
\include{appendices/appC_su3_primer}
\include{appendices/appD_poincare_disk}
\include{appendices/appE_tetrahedron_algebra}
\include{appendices/appF_baryon_calculations}
\include{appendices/appG_meson_calculations}
\include{appendices/appH_pdg_tables}
\include{appendices/appI_source_code}

%% ======================================================================
%% BIBLIOGRAPHY
%% ======================================================================
\begin{thebibliography}{99}

\bibitem{PDG2024}
S.~Navas \emph{et al.} (Particle Data Group),
``Review of Particle Physics,''
Phys.\ Rev.\ D \textbf{110}, 030001 (2024).

\bibitem{crewther1979}
R.~J.~Crewther, P.~Di~Vecchia, G.~Veneziano, and E.~Witten,
``Chiral estimate of the electric dipole moment of the neutron in
quantum chromodynamics,''
Phys.\ Lett.\ B \textbf{88}, 123 (1979).

\bibitem{pospelov2005}
M.~Pospelov and A.~Ritz,
``Electric dipole moments as probes of new physics,''
Ann.\ Phys.\ (N.Y.) \textbf{318}, 119 (2005).

\bibitem{Planck2018}
N.~Aghanim \emph{et al.} (Planck Collaboration),
``Planck 2018 results. VI. Cosmological parameters,''
Astron.\ Astrophys.\ \textbf{641}, A6 (2020).

\bibitem{gellmann1961}
M.~Gell-Mann,
``The eightfold way: A theory of strong interaction symmetry,''
Caltech Synchrotron Laboratory Report CTSL-20 (1961).

\bibitem{okubo1962}
S.~Okubo,
``Note on unitary symmetry in strong interactions,''
Prog.\ Theor.\ Phys.\ \textbf{27}, 949 (1962).

\bibitem{berry1984}
M.~V.~Berry,
``Quantal phase factors accompanying adiabatic changes,''
Proc.\ R.\ Soc.\ Lond.\ A \textbf{392}, 45 (1984).

\bibitem{witten1982}
E.~Witten,
``An SU(2) anomaly,''
Phys.\ Lett.\ B \textbf{117}, 324 (1982).

\bibitem{kobayashi1973}
M.~Kobayashi and T.~Maskawa,
``CP-violation in the renormalizable theory of weak interaction,''
Prog.\ Theor.\ Phys.\ \textbf{49}, 652 (1973).

\bibitem{pontryagin1955}
L.~S.~Pontryagin,
``Smooth manifolds and their applications in homotopy theory,''
Trudy Mat.\ Inst.\ Steklov \textbf{45}, 1 (1955).

\bibitem{shannon1948}
C.~E.~Shannon,
``A mathematical theory of communication,''
Bell Syst.\ Tech.\ J.\ \textbf{27}, 379 (1948).

\bibitem{t'Hooft1976}
G.~'t~Hooft,
``Symmetry breaking through Bell-Jackiw anomalies,''
Phys.\ Rev.\ Lett.\ \textbf{37}, 8 (1976).

\end{thebibliography}

\vfill
\noindent\small\textit{Source code and version history:}
\url{https://github.com/AdrianLipa90/The-Fundamental-Theory-of-Informational-Relations}
\par\vspace{2cm}

\backmatter
\printindex

\end{document}
