% !TEX root = ../metatime_monograph.tex
\chapter{Introduction}
\label{ch:introduction}

\section{The Problem of Parameters}

The Standard Model of particle physics stands as one of the most precisely tested
theories in the history of science.  Its predictions agree with experimental
measurements across energies ranging from fractions of an electronvolt to the
terascale at the Large Hadron Collider.  Yet the Standard Model, for all its
empirical success, leaves 19 numerical parameters unexplained: fermion masses
spanning six orders of magnitude, three gauge couplings, the Higgs mass and
vacuum expectation value, the CKM mixing angles and CP-violating phase, and
the QCD vacuum angle.  When neutrino masses and PMNS mixing parameters are
included, the count rises to 26.

These parameters are not predicted by the theory; they are measured and then
inserted by hand.  This situation has motivated decades of work on
parameter-reduction schemes: grand unified theories, supersymmetric extensions,
extra-dimensional models, and anthropic reasoning, among others.  None has
produced a consensus resolution.

\section{Quantum Geometry as the Foundation}

The present monograph develops a different approach---Metatime---in which
all Standard Model parameters are expressed through the geometry of quantum
state space itself.

The fundamental arena of quantum mechanics is not the classical spacetime
manifold but the \textbf{projective Hilbert space} \(\mathbb{C}P^{N-1}\),
the space of rays in an \(N\)-dimensional Hilbert space.  This is a
\textbf{K\"{a}hler manifold}: a complex manifold equipped with a
Hermitian metric whose imaginary part is a closed, non-degenerate
two-form---a symplectic structure.  Every quantum system naturally defines
such a geometry through its inner product.

The canonical metric on \(\mathbb{C}P^{N}\) is the
\textbf{Fubini--Study metric}:

\begin{equation}
ds_{\text{FS}}^2 = \frac{\langle d\psi|d\psi\rangle}{\langle\psi|\psi\rangle}
                 - \frac{|\langle\psi|d\psi\rangle|^2}{\langle\psi|\psi\rangle^2}.
\label{eq:fubini_study}
\end{equation}

Its real part gives the quantum geometric tensor (QGT), whose imaginary part
is the Berry curvature:

\[
\mathcal{F}_{\mu\nu} = i\,\text{Im}\,\langle\partial_\mu\psi|\partial_\nu\psi\rangle.
\]

The Berry phase accumulated by a quantum system under adiabatic cyclic
evolution is the integral of this curvature over a closed loop in parameter
space.  The Metatime constant \(\kappa\) is precisely such a Berry phase:

\[
\kappa = \frac{\ln 2}{24\pi},
\]

where \(\ln 2\) is the Shannon information entropy of a binary decision
(the fundamental unit of quantum information) and \(24\pi\) is the
symplectic volume of \(\mathbb{C}P^{3}\) (the projective Hilbert space of
three-flavour SU(3) colour).  The factor 24 arises from the order of the
tetrahedral group \(A_4\), which is the discrete holonomy group of the
Berry phase over the three-generation lepton structure.

Thus \(\kappa\) is not a free parameter but a \textbf{geometric invariant}
of the quantum state space, computed from first principles.

\section{The Metatime Framework}

Within this geometric setting, the framework is defined by:

\begin{equation}
\kappa \equiv \frac{\ln 2}{24\pi} \approx 9.19315 \times 10^{-3},
\label{eq:kappa_def}
\end{equation}

three integer L-constants (the dimensions of the K\"{a}hler submanifolds
that partition the quantum state space):

\begin{equation}
L_3 = 7,\qquad L_4 = 2,\qquad L_5 = 5,
\label{eq:L_defs}
\end{equation}

and six quark primes (the Chern class indices of the flavour fibres):

\begin{equation}
(u,d,s,c,b,t) = (3,5,7,11,13,17).
\label{eq:quark_primes_def}
\end{equation}

Two external energy scales enter: the Planck energy \(E_P = 1.22089\times
10^{22}\)~MeV (the natural scale of quantum gravity, at which the
Fubini--Study metric becomes non-perturbative) and the proton mass
\(E_{\text{proton}} = 938.272\)~MeV (the scale of hadronic confinement,
at which the K\"{a}hler curvature is integrated over the SU(3) fibre).

Three external numerical inputs complete the framework: the number of colours
\(N_c = 3\), the lepton hypercharge \(Y(L) = -1/2\), and the Crewther factor
\(2.4\times 10^{-16}\)~e\(\cdot\)cm (used for the neutron electric dipole
moment prediction).

\section{Philosophy of the Framework}

The Metatime framework is built on four principles:

\begin{enumerate}

\item \textbf{Information is K\"{a}hler geometry.}
The constant \(\kappa\) is the Berry phase---the holonomy of the
Fubini--Study connection on \(\mathbb{C}P^{3}\)---encoding the fundamental
trade-off between information gain (Shannon \(\ln 2\)) and symplectic volume
(\(24\pi\) for the colour octet).  Every mass formula is a K\"{a}hler
potential evaluated on a specific divisor of the quantum state space.

\item \textbf{Mass is action on the K\"{a}hler manifold.}
Every physical mass follows from the exponential formula

\[
m = E_P \, e^{-S/\kappa},
\]

where \(S\) is a K\"{a}hler action---the integrated curvature over a
two-cycle in the projective Hilbert space---constructed from prime-encoded
flavour states and the L-constants.

\item \textbf{Symmetry breaking is intersection theory.}
The SU(3) flavour symmetry and its breaking patterns (the Gell-Mann--Okubo
mass formula, CKM mixing, tetrahedral PMNS angles) are encoded in the
intersection numbers of K\"{a}hler submanifolds, expressed arithmetically
through the L-constants and quark primes.

\item \textbf{No continuous free parameters.}
Every numerical value in the framework is either a discrete structural
choice (the specific divisor combination in a formula) or a derivation from
those choices.  There are no continuous parameters fitted to experimental
data.  The scheme has the character of a
\textbf{quantum information-geometric bootstrap}: the state space geometry
dictates the particle spectrum.
\end{enumerate}

\section{Scope of This Monograph}

This monograph provides complete, step-by-step derivations for all ten sectors
of the Standard Model within the Metatime framework:

\begin{enumerate}
\item Charged lepton masses (Chapter~\ref{ch:lepton_spectrum}, mean error 0.48\%)
\item Baryon octet (Chapter~\ref{ch:octet_predictions}, mean error 1.72\%)
\item Baryon decuplet (Chapter~\ref{ch:decuplet_predictions}, mean error 0.34\%)
\item Pseudoscalar and vector mesons (Chapters~\ref{ch:pseudoscalar_mesons}, 0.07--0.58\%)
\item Neutrino PMNS mixing and masses (Chapters~\ref{ch:pmns_mixing}, all within \(1.6\sigma\))
\item CKM quark mixing matrix (Chapters~\ref{ch:ckm_matrix}, mean \(\sigma = 0.78\))
\item Electroweak gauge bosons and Higgs (Chapters~\ref{ch:gauge_bosons})
\item Strong CP angle and neutron EDM (Chapters~\ref{ch:strong_cp})
\item Gauge anomaly cancellation (Chapters~\ref{ch:anomaly_cancellation})
\item Cosmological constant (Chapter~\ref{ch:dark_energy}, error +3\%)
\end{enumerate}

No prior knowledge of the Metatime framework is assumed.  Every formula is
derived from \(\kappa\), the L-constants, and the quark primes, with all
intermediate algebraic steps shown.

\section{Relationship to Previous Work}

This monograph consolidates and completes a series of earlier reports
(versions v7.0 through v8.5) that established the individual sector formulas.
The key advances in the present version are:

\begin{itemize}
\item The baryon octet scale \(M_0\) is derived as
\(M_0 = E_{\text{proton}}(1 - (s+u)\kappa/L_3)\) (previously a free parameter).
\item The baryon decuplet scale \(M_0'\) is derived as
\(M_0' = E_{\text{proton}}(1 + (s-u)\kappa)\).
\item The fine-structure constant is derived as
\(1/\alpha = (L_3L_4)^2 - L_3^2 - L_4L_5 + L_4^2\kappa\) (previously an
external input).
\item All gauge sector parameters now depend solely on the same constants
as all other sectors.
\end{itemize}

All derivations are original to this work.  No claim is made that the
framework constitutes a fundamental physical theory; rather, it is presented
as a low-parameter ansatz---a systematic phenomenological pattern---that
reproduces the Standard Model parameter spectrum from the K\"{a}hler
geometry of quantum state space.
