% !TEX root = ../metatime_monograph.tex
\chapter{The Metatime Framework}
\label{ch:metatime_framework}

\section{The Information Constant \(\kappa\)}

The fundamental constant of the Metatime framework is the information
constant \(\kappa = \ln 2 / (24\pi)\).  We derive it from three ingredients:
the Berry phase of a spin-1/2 system, the Shannon information of a binary
decision, and the tetrahedral symmetry of three-flavour space.

\subsection{Berry Phase on the Poincar\'{e} Disk}

Consider a two-level quantum system (a spin-1/2 particle) whose Hamiltonian
depends adiabatically on parameters \(\mathbf{R}(t)\).  After the parameters
complete a closed cycle in parameter space, the system acquires a geometric
phase---the Berry phase~\cite{berry1984}:

\begin{equation}
\gamma_n = i \oint \langle n(\mathbf{R}) | \nabla_{\mathbf{R}} n(\mathbf{R}) \rangle \cdot d\mathbf{R}.
\label{eq:berry_general}
\end{equation}

For a spin-1/2 system, the parameter space is the Bloch sphere.
A cycle that subtends a solid angle \(\Omega\) yields a Berry phase
\(\gamma = \Omega/2\).  For a complete cycle \((\Omega = 4\pi)\), the Berry
phase is:

\begin{equation}
\gamma_{\text{spin}} = \frac{4\pi}{2} = \pi.
\label{eq:berry_spin_half}
\end{equation}

This is the natural geometric phase unit for a two-state quantum system.

\subsection{Shannon Information}

The information gained by resolving a binary outcome (e.g.\ a spin
measurement) is~\cite{shannon1948}:

\begin{equation}
I = \ln 2 \quad \text{(nats)}.
\label{eq:shannon_binary}
\end{equation}

This is the fundamental unit of information for a two-outcome measurement.

\subsection{Tetrahedral Symmetry of Three-Flavour Space}

The three-flavour structure of quarks and leptons (the three generations)
is associated with the tetrahedral symmetry group.  The full tetrahedral
symmetry group (including reflections) is \(S_4\), the symmetric group of
four objects, with order 24.  (The rotational subgroup is \(A_4\) of order
12.)

The number 24 emerges as the discrete holonomy constraint: the three-flavour
space is minimally quantized by the tetrahedral order.  (Note: the Weyl group
of SU(3) is \(S_3\) of order 6, a different group; the use of \(S_4\) here
reflects the tetrahedral NOEMA phase-space geometry, not the SU(3) root
system.)

\subsection{Construction of \(\kappa\)}

The information constant \(\kappa\) combines these three ingredients:

\begin{enumerate}
\item The Shannon information of a binary resolution: \(\ln 2\) (numerator,
encoding the information gained from a quantum measurement).
\item The Berry phase of a spin-1/2 cycle: \(\pi\) (denominator, representing
the geometric phase accumulated during one adiabatic cycle).
\item The tetrahedral holonomy: 24 (denominator, normalizing the three-flavour
discrete phase space).
\end{enumerate}

Thus:

\begin{equation}
\kappa \equiv \frac{\ln 2}{24\pi}.
\label{eq:kappa_construction}
\end{equation}

\noindent Evaluating numerically:

\[
\kappa = \frac{0.6931471805599453}{24 \times 3.141592653589793}
       = \frac{0.6931471805599453}{75.39822368615503}
       = 0.009193150006360484.
\]

\noindent For most purposes, we use the approximation \(\kappa \approx
9.19315 \times 10^{-3}\).

\section{The Exponential Mass Formula}

The central postulate of the Metatime framework is that every physical mass
is determined by an action \(S\) on the Poincar\'{e} disk via an exponential
Boltzmann-like factor:

\begin{equation}
m = E_P \, e^{-S/\kappa}.
\label{eq:mass_formula}
\end{equation}

Here \(E_P = \sqrt{\hbar c^5 / G} = 1.22089 \times 10^{22}\)~MeV is the Planck
energy (the fundamental scale of quantum gravity), and \(S\) is a
dimensionless action constructed from the L-constants and quark primes.

The exponential form arises from the geometric accumulation of phase on the
Poincar\'{e} disk.  The action \(S\) is an entropy-like sum over flavour
states, and the Boltzmann factor \(\exp(-S/\kappa)\) converts this action into
a physical mass scale.

\subsection{Why the Exponential Form?}

Consider a quantum system on the Poincar\'{e} disk with a discrete set of
accessible states.  The partition function is:

\[
Z = \sum_i e^{-E_i / k_B T}.
\]

In the geometric setting, the information constant \(\kappa\) plays the role
of \(k_B T\) (the fundamental action quantum), and the mass \(m\) plays the
role of the energy scale.  The action \(S\) encodes the number of accessible
states: a larger action (more information) corresponds to a lighter particle,
and a smaller action corresponds to a heavier particle.

\section{Action Construction Principles}

Each particle's action \(S\) is built from the following elements:

\begin{enumerate}
\item \textbf{Spin degeneracy:} A term \(\frac{1}{2}\) for spin-1/2 fermions,
encoding the two spin states.
\item \textbf{Generation terms:} Terms proportional to \(\kappa\) for each
generation, representing the information deficit shared across generations.
\item \textbf{Flavour terms:} Terms involving quark primes \(q_i\) and
L-constants \(L_3, L_4, L_5\), encoding the flavour structure.
\item \textbf{Geometric corrections:} Terms involving ratios of L-constants
and powers of \(\kappa\), representing higher-order curvature corrections on
the Poincar\'{e} disk.
\end{enumerate}

\section{The NOEMA Tetrahedron}

The NOEMA (Neutral Operator Eigenvalue Mapping Algebra) tetrahedron is a
geometric construction in the three-dimensional operator space spanned by:

\[
\{\hat I,\ \hat M,\ \hat A\},
\]

where \(\hat I\) is the isospin operator, \(\hat M\) is the mass operator,
and \(\hat A\) is the axial operator.  The tetrahedron encodes the mixing
patterns of quarks and leptons:

\begin{itemize}
\item The edge lengths are determined by \(L_3\) and \(L_4\).
\item The face areas determine mass splittings.
\item The dihedral angles determine mixing angles.
\end{itemize}

The NOEMA tetrahedron provides a unified geometric origin for the CKM and
PMNS mixing matrices, as we show in Chapters~\ref{ch:ckm_matrix} and
\ref{ch:pmns_mixing}.

\section{External Scales and Inputs}

The framework requires two external energy scales and three external numerical
inputs:

\begin{description}
\item[\(E_P = 1.22089 \times 10^{22}\)~MeV:] The Planck energy, setting the
absolute mass scale via the exponential formula.
\item[\(E_{\text{proton}} = 938.272\)~MeV:] The proton mass, used as the
reference scale for baryonic and electroweak quantities.
\item[\(N_c = 3\):] The number of colours in QCD, needed for hypercharge
assignments and anomaly cancellation.
\item[\(Y(L) = -1/2\):] The lepton doublet hypercharge, required for anomaly
cancellation checks.
\item[\(\text{Crewther factor} = 2.4 \times 10^{-16}\):] The chiral
perturbation theory factor relating \(\theta_{\text{QCD}}\) to the neutron
electric dipole moment.
\end{description}

All other numerical quantities are derived from \(\kappa\), the L-constants,
and the quark primes, with no continuous parameters fitted to data.
