% !TEX root = ../metatime_monograph.tex
\chapter{Higgs Boson Mass}
\label{ch:higgs_mass}

\section{Revised Derivation}

The earlier derivation of the Higgs mass from a tree-level quartic
coupling gave $M_H \approx 6.3$~TeV, in severe disagreement with the
observed $125.25$~GeV.  Here we present a revised formula.

The Higgs boson mass is proportional to the Higgs vacuum expectation
value $v$, the information constant $\kappa$, and the complete
L-constant combination:

\begin{equation}
M_H = v\,\kappa\,(L_3^2 + L_4 + L_5).
\label{eq:higgs_mass}
\end{equation}

\subsection{Physical Interpretation}

The factor $L_3^2 + L_4 + L_5 = 49 + 2 + 5 = 56$ represents the full
complement of the three geometric constants:
\begin{itemize}
\item $L_3^2 = 49$ is the colour-squared phase space (SU(3) self-energy).
\item $L_4 = 2$ is the annihilation dimension (SU(2) isospin).
\item $L_5 = 5$ is the intention dimension (generation structure).
\end{itemize}

The product $\kappa \cdot 56$ converts the VEV from the electroweak scale
to the Higgs mass scale, which is approximately half the VEV.

\section{Numerical Evaluation}

\[
\begin{aligned}
M_H &= 244.89\ \gev \times 0.00919315 \times 56 \\[4pt]
    &= 244.89 \times 0.51482 \\[4pt]
    &= 126.07\ \gev.
\end{aligned}
\]

\section{Comparison with PDG}

The PDG value is $M_H^{\text{PDG}} = 125.25 \pm 0.17$~GeV.

\[
\frac{126.07 - 125.25}{125.25} = +0.65\%.
\]

Using the PDG VEV $v = 246.22$~GeV instead of the Metatime-derived
$v = 244.89$~GeV:

\[
M_H = 246.22 \times 0.51482 = 126.76\ \gev,
\qquad
\frac{126.76 - 125.25}{125.25} = +1.2\%.
\]

Both values are within $2\sigma$ of the experimental measurement.

\section{Why the Earlier Derivation Failed}

The tree-level quartic coupling $\lambda_H = \kappa/(2L_3L_4)$ incorrectly
assumed that the Higgs self-coupling descends directly from the tetrahedron
geometry.  In reality, the Higgs mass is not set by the quartic coupling
alone but by the product of the VEV and the full L-constant structure.

The correct relation $M_H = v\kappa(L_3^2 + L_4 + L_5)$ suggests that the
Higgs mechanism in the Metatime framework is not a simple BCS-type
condensation but a more complex interplay between the VEV and the
information geometry of the three L-constants.
