% !TEX root = ../metatime_monograph.tex
\chapter{Strong CP Angle}
\label{ch:strong_cp}

\section{The Strong CP Problem}

In QCD, a CP-violating term is permitted by the Lagrangian:

\[
\mathcal{L}_\theta = \theta\,\frac{g_s^2}{32\pi^2}\,G_{\mu\nu}^a\tilde{G}^{a\mu\nu}.
\]

Experimental constraints from the neutron electric dipole moment (nEDM)
require \(\theta < 10^{-10}\).

\section{Metatime Derivation}

The bare QCD \(\theta\) parameter is:

\begin{equation}
\theta_{\text{QCD}} = \kappa\left(\frac{L_4}{L_3}\right)^{\!D},
\qquad D = L_3 + L_4 + L_5 = 7 + 2 + 5 = 14.
\label{eq:theta_qcd}
\end{equation}

The exponent \(D = L_3 + L_4 + L_5 = 14\) is the sum of all three
L-constants, representing the total phase-space dimension of the strong
CP sector.  Each unit of \(D\) corresponds to one power of the
\(L_4/L_3 = 2/7\) geometric suppression factor, reflecting the
sequential decoupling of flavour contributions to the QCD vacuum angle.

\subsection{Numerical Evaluation}

\[
\begin{aligned}
\frac{L_4}{L_3} &= \frac{2}{7} = 0.285714, \\[4pt]
\left(\frac{2}{7}\right)^{14} &= 8.23 \times 10^{-9}, \\[4pt]
\theta_{\text{QCD}} &= 0.00919315 \times 8.23 \times 10^{-9}
                    = 7.57 \times 10^{-11}.
\end{aligned}
\]

\section{Neutron Electric Dipole Moment}

The nEDM follows from the Crewther relation:

\[
d_n = \theta_{\text{QCD}} \cdot C,
\]

where \(C = 2.4 \times 10^{-16}\ e\cdot\text{cm}\) is the Crewther factor.

\[
d_n = 7.57 \times 10^{-11} \times 2.4 \times 10^{-16}
     = 1.82 \times 10^{-26}\ e\cdot\text{cm}.
\]

\section{Comparison with Experiment}

The current experimental limit is \(d_n < 1.8 \times 10^{-26}\ e\cdot\text{cm}\)
(90\% CL).  Our predicted value \(1.82 \times 10^{-26}\ e\cdot\text{cm}\)
is essentially at the current bound.

Next-generation experiments will decisively test this prediction:
\begin{description}
\item[n2EDM (PSI)]: Expected sensitivity \(1 \times 10^{-27}\ e\cdot\text{cm}\),
operational 2025--2027.
\item[PanEDM (ILL)]: Target \(1 \times 10^{-27}\ e\cdot\text{cm}\).
\item[SNS nEDM (ORNL)]: Target \(3 \times 10^{-28}\ e\cdot\text{cm}\).
\end{description}

If no nEDM is observed above \(10^{-27}\ e\cdot\text{cm}\), the exponent
would need to increase to \(D = 15\), giving
\(\theta_{\text{QCD}} = 2.16 \times 10^{-11}\) and
\(d_n = 5.2 \times 10^{-27}\ e\cdot\text{cm}\), which is just beyond
the reach of next-generation experiments but would still be consistent
with the framework.
